Pillar 2- Quick Topic Models

### 2019-04-23 Pillar 2 - Tmp Topic Modeling.Rmd
evaluate over many models catalogues

#Training
topic_numbers <-c(50, 55, 60, 65, 70) #seq(from = 5, to = 10, by = 2) #5 to 150 by 50
which_texts <- "catalogues"

@@

#Plot
plot_evaluation("catalogues")
plot_evaluation("manuals")
```
##Different alphas and delta (prior of term distributions over topics)
To evaluate the impact of the initial alpha and beta on our model, we train the model using different inizialization values for alpha and delta. Note that this is only an inizialisation and the algorithm will try to extimate alpha and beta.
###Alpha
```{r alpha, eval = FALSE}
sample_dtm <- tb_topic_model$DTM[[1]] #1 CATALOGUES, 2 MANUALS

>>>>

#Training
topic_numbers <-seq(from = 5, to = 150, by = 5)#c(50, 55, 60, 65, 70) #seq(from = 5, to = 10, by = 2) #5 to 150 by 50
which_texts <- "catalogues"

@@

#Plot
plot_evaluation("catalogues")
#plot_evaluation("manuals")
```
##Different alphas and delta (prior of term distributions over topics)
To evaluate the impact of the initial alpha and beta on our model, we train the model using different inizialization values for alpha and delta. Note that this is only an inizialisation and the algorithm will try to extimate alpha and beta.
###Alpha
```{r alpha, eval = FALSE}
sample_dtm <- tb_topic_model$DTM[[1]] #1 CATALOGUES, 2 MANUALS
